Report

### 2021-07-23 Rmd/report.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

# load objects
tar_load(participants)
tar_load(stimuli)
tar_load(vocabulary)

# stringent version
tar_load(gaze)
tar_load(attrition)
tar_load(fit)
tar_load(fit_21_mon)
tar_load(fit_21_mon_vocab_split)
tar_load(fit_21_mon_vocab_balanced)
tar_load(fit_21_mon_location)

# relaxed version
tar_load(gaze_relaxed)
tar_load(attrition_relaxed)
tar_load(fit_relaxed)
tar_load(fit_21_mon_relaxed)
tar_load(fit_21_mon_vocab_split_relaxed)
tar_load(fit_21_mon_vocab_balanced_relaxed)
tar_load(fit_21_mon_location_relaxed)

@@

@@

@@

```{r child="report_07_raw_relaxed.Rmd"}
```

@@

@@

>>>>

# load objects
tar_load(participants)
tar_load(stimuli)
tar_load(vocabulary)
tar_load(gaze)
tar_load(gaze_relaxed)
tar_load(attrition)
tar_load(attrition_relaxed)
tar_load(attrition_counter)
tar_load(attrition_relaxed_counter)
tar_load(model_fits)
tar_load(model_fits_relaxed)

@@

attrition_counter <- attrition_counter %>% 
	mutate(
		valid_gaze = valid_gaze_prime & valid_gaze_target,
		valid_status = case_when(
			!valid_vocab ~ "Invalid vocabulary",
			!valid_gaze ~ "Invalid gaze",
			!valid_participant ~ "Invalid participant",
			!valid_counter ~ "Invalid counter",
			TRUE ~ "Valid"
		))

attrition_relaxed_counter <- attrition_relaxed_counter %>% 
	mutate(
		valid_gaze = valid_gaze_prime & valid_gaze_target,
		valid_status = case_when(
			!valid_vocab ~ "Invalid vocabulary",
			!valid_gaze ~ "Invalid gaze",
			!valid_participant ~ "Invalid participant",
			!valid_counter ~ "Invalid counter",
			TRUE ~ "Valid"
		))

@@

participants_counter <- participants %>% 
	left_join(distinct(attrition_counter, participant, age_group, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocabulary) %>% 
	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])

participants_relaxed_counter <- participants %>% 
	left_join(distinct(attrition_relaxed_counter, participant, age_group, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocabulary) %>% 
	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])

@@

@@

## Attrition {.tabset}

@@

### Counterbalancing {.tabset}

#### Stringent criteria {.tabset}

```{r child="report_05_attrition_counter_stringent.Rmd"}
```

#### Relaxed criteria {.tabset}

```{r child="report_05_attrition_counter_relaxed.Rmd"}
```

#### {-}

## 21 months-old monolinguals {.tabset}

### 2021-07-23 Rmd/report_00_participants_relaxed.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

>>>>

```{r participants_summary_relaxed_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_relaxed %>% 
	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	count(location, age_group, lp) %>% 
	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
	gt(groupname_col = "location") %>% 
	cols_label(
		lp = md("**Language profile**"),
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	)

```

### 2021-07-23 Rmd/report_00_participants_stringent.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

>>>>

```{r participants_summary_stringent_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_relaxed %>% 
	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	count(location, age_group, lp) %>% 
	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
	gt(groupname_col = "location") %>% 
	cols_label(
		lp = md("**Language profile**"),
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	)

```

### 2021-07-23 Rmd/report_01_stimuli.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

## Stimuli {.tabset }

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(trial_type, frequency_prime_subtlex, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language) +
	geom_violin() +
	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
	geom_jitter(colour = "black", size = 1, shape = 1,
				width = 0.1, alpha = 0.5, stroke = 1) +
	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", fill = "Trial type") +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(trial_type, frequency_target_subtlex, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language) +
	geom_violin() +
	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
	geom_jitter(colour = "black", size = 1, shape = 1,
				width = 0.1, alpha = 0.5, stroke = 1) +
	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", fill = "Trial type") +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		plot.caption = element_text(size = 10, hjust = 0),
	)
```

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	# mutate(prime = reorder_within(target, familiarity_prime, list(location, test_language))) %>% 
	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime), colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language, scales = "free_y") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
	# geom_errorbar() +
	geom_point() +
	labs(x = "% of infants that understand", y = "Prime word",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent) +
	# scale_y_reordered() +
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(familiarity_target, reorder(target, familiarity_target), colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language, scales = "free_y") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
	# geom_errorbar() +
	geom_point() +
	labs(x = "% of infants that understand", y = "Target word",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent) +
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

	plot_layout(guides = "collect", ncol = 1) &
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.y = element_blank(),
		axis.text = element_text(size = 10),
		strip.text = element_text(size = 11)
	)

>>>>

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(trial_type, frequency_prime_subtlex, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language) +
	geom_violin() +
	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
	geom_jitter(colour = "black", size = 1, shape = 1,
				width = 0.1, alpha = 0.5, stroke = 1) +
	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", fill = "Trial type") +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 7),
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(trial_type, frequency_target_subtlex, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language) +
	geom_violin() +
	geom_boxplot(colour = "black", fill = "white", outlier.colour = NA, width = 0.1) +
	geom_jitter(colour = "black", size = 1, shape = 1,
				width = 0.1, alpha = 0.5, stroke = 1) +
	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", fill = "Trial type") +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 7),
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		plot.caption = element_text(size = 10, hjust = 0),
	)
```

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	# mutate(prime = reorder_within(target, familiarity_prime, list(location, test_language))) %>% 
	ggplot(aes(familiarity_prime, reorder(prime, familiarity_prime),  colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language, scales = "free_y") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(data = means, aes(xintercept = familiarity_prime, colour = trial_type), size = 1) +
	# geom_errorbar() +
	geom_point() +
	labs(x = "% of infants that understand", y = "Prime word",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 7),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(familiarity_target, reorder(target, familiarity_target), colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language, scales = "free_y") +
	geom_vline(xintercept = 0.5, size = 1, colour = "grey") +
	geom_vline(data = means, aes(xintercept = familiarity_target, colour = trial_type), size = 1) +
	# geom_errorbar() +
	geom_point() +
	labs(x = "% of infants that understand", y = "Target word",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent, limits = c(0, 1)) +
	# scale_y_reordered() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 7),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

	plot_layout(guides = "collect", ncol = 1) &
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		strip.text = element_text(size = 11)
	)

### 2021-07-23 Rmd/report_04_gca_relaxed.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets

### Growth curve analysis {.tabset}

@@

```{r fixed_effects_table_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_relaxed, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_relaxed, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

@@

VarCorr(fit_relaxed)$participant %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	gt(rowname_col = "term1") %>% 
	fmt_number(columns = 2:9) %>% 
	data_color(
		columns = 2:9,
		colors = col_numeric(
			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
			domain = c(-1, 1), alpha = 0.5
		)
	)

@@

augment(fit_relaxed) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups. Sample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme_custom() +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7),
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	) 
```

@@

augment(fit_relaxed) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size_l1_center <= median(.$vocab_size_l1_center)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size <= median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

@@

augment(fit_relaxed) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size > median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

@@

augment(fit_relaxed) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Barcelona") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

@@

augment(fit_relaxed) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(y = .fitted_prob, colour = trial_type, fill = trial_type), fun = mean, geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Oxford") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

>>>>

```{r define_model_relaxed, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
fit <- model_fits_relaxed$fit
fit_21_mon <- model_fits_relaxed$fit_21_mon
fit_21_mon_location <- model_fits_relaxed$fit_21_mon_location
fit_21_mon_vocab_split<- model_fits_relaxed$fit_21_mon_vocab_split
fit_21_mon_vocab_balanced <- model_fits_relaxed$fit_21_mon_vocab_balanced
```

@@

```{r fixed_effects_table_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#ffc7a1")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

@@

VarCorr(fit)$participant %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	gt(rowname_col = "term1") %>% 
	fmt_number(columns = 2:9) %>% 
	data_color(
		columns = 2:9,
		colors = col_numeric(
			palette = RColorBrewer::brewer.pal(n = 9, name = "Oranges"),
			domain = c(-1, 1), alpha = 0.5
		)
	)

@@

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob,
					 group = interaction(participant, trial_type),
					 colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups. Sample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme_custom() +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7),
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	) 
```

@@

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size_l1_center <= median(.$vocab_size_l1_center)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob,
					 group = interaction(participant, trial_type),
					 colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size <= median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

@@

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size_l1_center > median(.$vocab_size_l1_center)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob,
					 group = interaction(participant, trial_type),
					 colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size > median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

@@

augment(fit) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob,
					 group = interaction(participant, trial_type),
					 colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Barcelona") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

@@

augment(fit) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob,
					 group = interaction(participant, trial_type),
					 colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", alpha = 0.25, size = 0.5) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	stat_summary(aes(x = ot1, y = logit_to_prob(elog), colour = trial_type, fill = trial_type), fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Oxford") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze_relaxed$ot1), labels = unique(gaze_relaxed$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```
